### 2022-06-13 paper.tex
draft for abstract

June 2022
\vspace{6ex}
}]
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mail:  \texttt{l.kremer@dkfz-heidelberg.de} and\\ \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}
\section{Abstract}

[...]

>>>>

June 2022
\vspace{6ex}
}]
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mail:  \texttt{l.kremer@dkfz-heidelberg.de} and\\ \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}

\section{Abstract}

Single-cell-bisulfite sequencing (scBS) allows to asses DNA methylation with single-basepair and single-cell resolution. Analysing the big data sets thus obtained requires preprocessing to reduce data size, improve signal over noise, and provide interpretability. Currently, this is simply done by tiling teh genome into large windows and averaging in these. We show that this coarse-graining dilutes signal, and suggest improved approaches to determine informative regions to quantify for and to quantitate methylation in these windows. We demonstrate how our preprocessing approach helps to better distinguish cell types, reduces demands on cell number, and show that our method of finding variably-methylated regions finds biologically meaningful loci. Finally, we present a software tool, \texttt{scbs}, that implements this approach and offers further functionality requried to work with scBS data.
